Revision Plan for SIGCOMM'24 Paper \#293

### 2024-05-20 revision_plan.tex
update all

\noindent\textcolor{blue}{\textbf{Response A.1:}
Thanks for the reviewer’s comments. 
PPT uses eight strict priorities in the switch.
To prevent HCP traffic harmed by LCP, priorities 0$\sim$3 are used to transmit HCP packets, and priorities 4$\sim$7 are used to transmit LCP packets.
Therefore, the \emph{high-priority} and \emph{low-priority} mentioned in p.6 and p.9 refer to priorities 0$\sim$3 and 4$\sim$7 in the switch, respectively.
To avoid ambiguity, we will include footnotes in Section 3.2 for explanation.
}

@@

\noindent\textcolor{blue}{\textbf{Response A.2:}
Thanks for the reviewer's comments. 
Although very sorry, the reviewer seems to have misinterpreted PPT's strategy.
At the beginning of Section 3, we mentioned that "LCP sends opportunistic packets from the tail end."
Therefore, both HCP and LCP send data in the same flow.
However, many of the review's comments were based on LCP and HCP transmitting data from different flows, which made it difficult for us to answer.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.1:}
Thanks for the reviewer’s comments. 
Since the NIC rate can be read via system call and the datacenter network topology is relatively fixed, we assume the RTT is known a priori.
By NIC rate times RTT, we assume the host knows the BDP in advance.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.2:}
Thanks for the reviewer’s comments. 
During the process of congestion subsiding, the switch queue length is reduced, the percentage of ECN marked packets for this long flow decreases, and the value of $\alpha$.
As the congestion subsides completely, the proportion of ECN-marked packets should be 0.
PPT initializes LCP for the long flow whenever $\alpha$ takes the minimum value.
At this point, $\alpha$ must be less than 0.5, which makes this large flow utilize the spare bandwidth.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.3:}
Thanks for the reviewer’s comments. 
}

@@

\noindent\textcolor{blue}{\textbf{Response B.4:}
Thanks for the reviewer’s comments. 
We will add a new simulation experiment with topology consisting of 144 servers, 9 leaf switches, and 4 spine switches, with the host and core links operated at 400 and 1000Gbps, respectively.
We will plot the results in the appendix.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.5:}
Thanks for the reviewer’s comments. 
Actually, we measure the kernel space CPU overhead of PPT and DCTCP in our testbed.
We plot the results in Figure 21.
For more details, please read Appendix C.1.
}

@@

\noindent\textcolor{blue}{\textbf{Response C.2:}
Thanks for the reviewer’s comments. 
After carefully checking our data processing code, we found that under Datamining workloads, RC3 would result in a few flows not completing due to many packet losses.
Our code incorrectly used the program runtime as the flow completion time when calculating the overall average FCT, resulting in the actual computed result being larger.
We will fix the bug and update the correct result.
}

@@

\noindent\textcolor{blue}{\textbf{Response C.3:}
Thanks for the reviewer's comments. 
Although limiting the RC3 low-priority queue can prevent the LCP from sending too many opportunity packets, the following reasons still lead to low performance.
First, during the slow-start phase of the flow, limiting the buffer LCP could use will leave a large amount of bandwidth underutilized.
Second, RC3 keeps the LCP open instead of intermittent initialization as PPT, which causes more severe congestion during traffic bursts.
Last but not least, RC3's lack of using in-network priority causes small flow packets to be queued after LCP packets, increasing small flow latency.
We will add the above analyses to our paper.
}

@@

\noindent\textcolor{blue}{\textbf{Response D.1:}
Thanks for the reviewer’s comments. 
As mentioned in Section 6.1.2, Homa-Linux sends BDP-sized unscheduled packets for each arriving flow, and excessive opportunity packets cause heavier congestion in incast scenarios.
Furthermore, Homa-Linux is connectionless, so packet loss recovery is achieved through retransmission after timeout.
Large packet loss in Incast scenarios further impairs its performance.
We will add more detailed analyses in the paper.
}

@@

\noindent\textcolor{blue}{\textbf{Response E.1:}
Thanks for the reviewer’s comments. 
In our paper, we construct a stricter variant of PPT that assigns all packets the same priority.
We plot the results in Figure 19.
Even under these conditions, we find that PPT still achieves the optimal overall average FCT among NDP, Homa, Aeolus, DCTCP, and RC3.
}

@@

\noindent\textcolor{blue}{\textbf{Response E.2}
Thanks for the reviewer’s comments. 
We will add a large-scale simulation experiment with 2k nodes to the appendix.
}

>>>>

\noindent\textcolor{blue}{\textbf{Response A.1:}
Thanks for the reviewer’s comments. 
To avoid ambiguity, we will include footnotes in Section 3.2 for explanation.
PPT uses eight strict priorities in the switch.
To prevent HCP traffic harmed by LCP, priorities 0$\sim$3 are used to transmit HCP packets, and priorities 4$\sim$7 are used to transmit LCP packets.
Therefore, the \emph{high-priority} and \emph{low-priority} mentioned in p.6 and p.9 refer to priorities 0$\sim$3 and 4$\sim$7 in the switch, respectively.
}

@@

\noindent\textcolor{blue}{\textbf{Response A.2:}
Thanks for the reviewer's comments. 
At the beginning of Section 3, we mentioned that "LCP sends opportunistic packets from the tail end."
Therefore, HCP and LCP send packets from the beginning and end of the same flow, respectively.
So, there is no scenario in which there is no HCP flow.
Since HCP and LCP come from the same flow, they must have the same number and destination.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.1:}
Thanks for the reviewer’s comments. 
Since $BDP = rtt*rate_{nic}$.
While the $rate_{nic}$ can be read via system call and the datacenter network topology is relatively fixed, we assume the $rtt$ is known a priori.
So we can calculate the BDP in advance.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.2:}
Thanks for the reviewer’s comments. 
Actually, it is very rarely in our experiments that $\alpha$ is greater than 0.5, as it requires the number of ECN marked packets to be more than half of the number of all packets over many sequential RTTs.
While $\alpha$ greater than 0.5 represents the link experienced severe congestion, there is no spare bandwidth for LCP.
%During the process of congestion subsiding, the switch queue length is reduced, the percentage of ECN marked packets for this long flow decreases, and the value of $\alpha$.
%As the congestion subsides completely, the proportion of ECN-marked packets should be 0.
%PPT initializes LCP for the long flow whenever $\alpha$ takes the minimum value.
%At this point, $\alpha$ must be less than 0.5, which makes this large flow utilize the spare bandwidth.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.3:}
Thanks for the reviewer’s comments. 
It is true that we have not taken into account the fairness issue in this scenario, but it can be solved by a simple design.
We will discuss this in Appendix A.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.4:}
Thanks for the reviewer’s comments. 
We will add a new simulation experiment with topology consisting of 144 servers, 9 leaf switches, and 4 spine switches, with the host and core links operated at 100 and 400Gbps, respectively.
We will plot the results in the appendix.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.5:}
Thanks for the reviewer’s comments. 
We measure the kernel space CPU overhead of PPT and DCTCP in our testbed.
We plot the results in Figure 21.
For more details, please read Appendix C.1.
}

@@

\noindent\textcolor{blue}{\textbf{Response C.2:}
Thanks for the reviewer’s comments. 
After we checked the experimental data we found that the results were error due to our input errors.
We will correct the error and double-check the rest of data.
%After carefully checking our data processing code, we found that under Datamining workloads, RC3 would result in a few flows not completing due to many packet losses.
%Our code incorrectly used the program runtime as the flow completion time when calculating the overall average FCT, resulting in the actual computed result being larger.
%We will fix the bug and update the correct result.
}

@@

\noindent\textcolor{blue}{\textbf{Response C.3:}
Thanks for the reviewer's comments. 
We will add intuitive reasons to Section 6.2.
%Although limiting the RC3 low-priority queue can prevent the LCP from sending too many opportunity packets, the following reasons still lead to low performance.
%First, during the slow-start phase of the flow, limiting the buffer LCP could use will leave a large amount of bandwidth underutilized.
%Second, RC3 keeps the LCP open instead of intermittent initialization as PPT, which causes more severe congestion during traffic bursts.
%Last but not least, RC3's lack of using in-network priority causes small flow packets to be queued after LCP packets, increasing small flow latency.
%We will add the above analyses to our paper.
}

@@

\noindent\textcolor{blue}{\textbf{Response D.1:}
Thanks for the reviewer's comments.
Homa's poor performance in the testbed is due to the inefficient implementation of the Homa-Linux network stack.
We have explained this in the \emph{remark} paragraph in Section 6.1.1.
%As mentioned in Section 6.1.2, Homa-Linux sends BDP-sized unscheduled packets for each arriving flow, and excessive opportunity packets cause heavier congestion in incast scenarios.
%Furthermore, Homa-Linux is connectionless, so packet loss recovery is achieved through retransmission after timeout.
%Large packet loss in Incast scenarios further impairs its performance.
%We will add more detailed analyses in the paper.
}

@@

\noindent\textcolor{blue}{\textbf{Response E.1:}
Thanks for the reviewer’s comments. 
In our paper, we have constructed the variant of PPT that assigns all packets with two priority queues.
We plot the results in Figure 19.
PPT still achieves the optimal overall average FCT among NDP, Homa, Aeolus, DCTCP, and RC3.
}

@@

\noindent\textcolor{blue}{\textbf{Response E.2}
Thanks for the reviewer’s comments. 
Our current topology is commonly used in academia.
Simulation experiments containing 2k nodes require significant time consumption, which we will implement in future work.
%We will add a large-scale simulation experiment with 2k nodes to the appendix.
}
